\documentclass[letterpaper,12pt]{article}
\usepackage[utf8]{inputenc}
%\usepackage[letterpaper, portrait, margin=1.0in]{geometry}
\usepackage{hyperref}

%opening
\title{Cross-platform Alternative to HomeOS Status Report 2}
\author{Christopher Becker and Shivam Kumar Sharma}

\begin{document}

\maketitle

\section*{Progress}
Since then last checkin we have done the following:
\begin{enumerate}
 \item We decided that for now we will only support the Z-Wave protocol. For all Z-Wave-specific functions we are using the OpenZWave library. The library is written in C++. There is a project on GitHub called zwave4j, where the author has created Java wrapper classes for all the classes in OpenZWave. We decided to use these wrapper classes so that our Java-based system can communicate with C++-based OpenZWave library. We faced a lot of difficulty in building zwave4j. If the OpenZWave directoy has been built, building zwave4j gives errors. After a lot of head scratching and searching online, Christopher was able to figure this out.
 \item Once we had built zwave4j, we developed a basic program to communicate with the light bulb. We are able to turn the light bulb on and off and control its brightness, but we are not able to change its color. After researching a little, we found out that the light bulb device that we have implements a Z-Wave class called ``ColorControl'' for controlling its color. The class is not supported by OpenZWave yet. Shivam tried to write some code to get around that, but was not successful in changing the color. Since it's not very important for our project to be able to change the color of the light bulb (since this is a limitation of the OpenZWave library rather than a limitation of our system), we decided to drop pursuing it for now.
 \item We have created an initial architecture of the system.
\end{enumerate}
On almost everything we worked together as much as possible.

We were able to achieve the goal that we had planned to accomplish at the previous project status report.

For the upcoming week our main goal is to finish coding the system. Since we have played around with Z-Wave and the light bulb, we feel we should be able to quickly code related aspects of our system. The main challenge will be in developing the access control related modules.
\end{document}
