\subsection*{Abstract}
Networked ``smart home'' devices such as remotely controlled lights, cameras,
thermostats, and locks have become relatively inexpensive and widely available.
While, in theory, this should allow the proliferation of these devices as well
as the ability to use them in a wide range of scenarios such as adjusting the
climate control settings of a room based on occupancy levels or remotely
controlling a device such as a camera through a smart phone. In practice this is
not the case. The overhead of managing and extending the current systems is
generally not reasonable for the population at large, but is reserved for
expert hobbyists and the wealthy. As part of the management of a home automation
system, access control is often difficult to correctly configure, especially in
systems with many devices and many users. The difficulty of configuring access
control rules leads to security and privacy issues.

Some recent work has been done in an attempt to rectify this disparity by
providing a PC-like abstraction to easily manage and extend systems to include
devices and allow a wide range of scenarios. One specific system, HomeOS, was
developed by Microsoft Research. HomeOS is designed to be a system which
presents devices as peripherals, uses applications to allow cross-device tasks,
provides a user interface designed to be used in a home environment, and an easy
to understand access control system. However, HomeOS only runs on Windows.  We
present an alternative to HomeOS which provides cross-platform support.