\section{Conclusion and Future Work}
\label{sec:future}
Our alternative to HomeOS continues the work started by HomeOS by providing
cross-platform support while still providing a PC-like abstraction for home
automation devices. Our alternative is written in Java and uses open source
software to try to maximize cross-platform capabilities. We have implemented the
core system, but more work is needed to provide all of the same capabilities as
HomeOS.

Future work includes adding additional functionality and continuing to expand
the API available to users and developers, as well as making extension of the
system easier. We talk about this in more detail below.

Currently our system only supports the Z-Wave protocol. We want
to add support for protcols like Bluetooth, Wi-Fi, ZigBee etc. We have device
drivers only for Zipato RGBW light bulb. We would like to add drivers for music
players, thermostat, security cameras, motion detectors etc. This will allow us
to create applications with richer funcionalities like ``start blinking the
light when some movement is detected by the motion sensor''.

We want to create an infrastructure that can allow the users to easily install
new components and roles. Similar to HomeOS we envisage having packages that
contain a Manifiest file and binaries. Our system will read the Manifest and
paste the binaries accordingly.

We want to give the user the capability to specify per user defaults for
components. For example if we have an application that can turn on the light
bulb and there are two light bulbs in the home one at the living room and one
at the bedroom. Currently the application will prompt the user to ask which one
to use. Instead now the user can save that preference and the application will
use that component by default in the future.

We plan to improve and expand the access control mechanisms and improve the user
interface, to improve both the usability and security of the system. We plan on
having the capability to create time based user accounts. If the owner has
relatives coming over, the owner can create accounts that will be active only
during the duration of the stay of the relatives. As of now we cannot force the
components to not to access the file system or the network. We want to add these
security features to our system.

We wish to add an online marketplace, to allow users to easily find applications
and drivers to extend and improve their systems. Similarly the developers can
upload their applications to the marketplace allowing easy access to the users.

Lastly we wish to create a more graphical and intuitive user interface which
will allow the user to easily extend, configure and query the system.
