\section{Introduction}
\label{sec:intro}
Networked ``smart home'' devices such as remotely controlled lights, cameras,
thermostats, and locks have become relatively inexpensive and widely available.
While, in theory, this should allow the proliferation of these devices as well
as the ability to use them in a wide range of scenarios such as adjusting the
climate control settings of a room based on occupancy levels or remotely
controlling a device such as a camera through a smart phone. In practice this is
not the case. The overhead of managing and extending the current systems is
generally not reasonable for the population at large, but is reserved for
expert hobbyists and the wealthy. As part of the management of a home automation
system, access control is often difficult to correctly configure, especially in
systems with many devices and many users. The difficulty of configuring access
control rules leads to security and privacy issues.

Some recent work has been done in an attempt to rectify this disparity by
providing a PC-like abstraction to easily manage and extend systems to include
devices and allow a wide range of scenarios. One specific system,
HomeOS~\cite{homeOS}, was developed by Microsoft Research. HomeOS is designed to
be a system which presents devices as peripherals, uses applications to allow
cross-device tasks, provides a user interface designed to be used in a home
environment, and an easy to understand access control system. However, HomeOS
only runs on Windows.

We present an alternative to HomeOS which provides cross-platform support. Our
main contribution is providing a cross-platform system, which uses open source
components, designed to have similar capabilities as those of HomeOS. We also
have made minor changes to the system which we feel will improve the overall
system.

The remainder of the paper is structured as follows: In
Section~\ref{sec:related}, we introduce related work, focusing on HomeOS. In
Section~\ref{sec:arch}, we provide an overview of the system architecture. In
Section~\ref{sec:implementation}, we provide details about our implementation
and current status. In Section~\ref{sec:homeosdiff}, we discuss the conceptual
differences between HomeOS and our system. In Section~\ref{sec:challenges}, we
highlight some of the challenges we faced in implementing the system. In
Section~\ref{sec:test}, we describe our testbed setup. In
Section~\ref{sec:future}, we discuss the results and future work. We conclude
with Section~\ref{sec:conclusion}.
